todo: think about good title

### 2019-01-05 documentation/paper.tex
More work-work

\subsection{Crossover}

As crossover we randomly mixed the nodes with belonging weights and biases of two networks and chose the parents via the fitness proportional roulette wheel selection.

\subsection{Mutation}

Mutation is accomplished by adding Gaussian noise to a subset of all weights and biases.

\subsection{Scheme}

Furthermore we implemented elitism.

fitness is the normalized point difference after $21$ serves.

@@

\begin{figure}[H]
\center
\begin{tabular}{ccc}
\texttt{reduced} & \texttt{com\_11} & \texttt{gintonicV9} \\
\includegraphics[width=0.3\textwidth]{img/standard_reduced.png} &
\includegraphics[width=0.3\textwidth]{img/standard_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/standard_gintonicV9.png} \\
\texttt{hyp014} & \texttt{Union} & \texttt{trainer} \\
\includegraphics[width=0.3\textwidth]{img/standard_hyp014.png} &
\includegraphics[width=0.3\textwidth]{img/standard_Union.png} &
\includegraphics[width=0.3\textwidth]{img/standard_trainer.png}
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:standard}
\end{figure}

>>>>

\subsection{Scheme}
The algorithm worked with a population size of 100, with 150 offspring after crossover. Our survivor selection strategy was elitism, selecting from the pool of children plus the 10 best parents from the last generation.

The fitness function was the normalized point difference after $21$ serves.

\subsection{Mutation}
Mutation is accomplished by adding Gaussian noise to a subset of all weights and biases. \todo{Default values, rate of change}

\subsection{Crossover}
As crossover we randomly mixed the nodes with belonging weights and biases of two networks and chose the parents via the fitness proportional roulette wheel selection. \todo{cite roulett wheel sel.}

@@

\begin{figure}[H]
\center
\begin{tabular}{ccc}
\texttt{reduced} & \texttt{com\_11} & \texttt{gintonicV9} \\
\includegraphics[width=0.3\textwidth]{img/standard_reduced.png} &
\includegraphics[width=0.3\textwidth]{img/standard_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/standard_gintonicV9.png} \\
\texttt{hyp014} & \texttt{Union} & \texttt{trainer} \\
\includegraphics[width=0.3\textwidth]{img/standard_hyp014.png} &
\includegraphics[width=0.3\textwidth]{img/standard_Union.png} &
\includegraphics[width=0.3\textwidth]{img/standard_trainer.png}
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum while training against different bots. \todo{is this true?}}
\label{fig:standard}
\end{figure}
